---
title: "ChatStat Report for `r Sys.Date()`"
params:
  test: true
  rooms: null
output:
  html_document:
    css: 'style.css'
    fig_width: 9
    fig_height: 4
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# We expect a rooms object as input.
rooms <- params$rooms

if (is.null(rooms)) {
  stop("No data provided!")
}
```

Statistics generated on `r Sys.time()` and based on data from the last 30 days.

This data has a total of **`r length(unique(rooms$events$sender))`** different
IDs, speaking a total of **`r nrow(rooms$events)`** messages.

### Daily Activity & trend

```{r}
plot_daily_activity(rooms)
```

### Daily Activity, breakdown by time-of-day

```{r}
plot_time_of_day_activity(rooms)
```

### Most active times

```{r}
plot_active_times(rooms)
```

### Top ten posters (by message count)

Words like "and", "the", "or", and so on have been removed before
counting.

```{r}
rooms$events |>
  dplyr::filter(type == "m.room.message" & !is.na(body)) |>
  dplyr::group_by(sender) |>
  tidytext::unnest_tokens(
    output = "word",
    input = body,
    drop = FALSE
  ) |>
  dplyr::filter(!(word %in% tidytext::stop_words$word)) |>
  dplyr::add_count(sender, name = "words") |>
  dplyr::group_by(sender) |>
  dplyr::slice_sample(n = 1) |>
  dplyr::left_join(
    dplyr::count(rooms$events, sender, name = "messages"),
    by = "sender"
  ) |>
  dplyr::arrange(-messages) |>
  dplyr::select(-word) |>
  dplyr::ungroup() |>
  dplyr::slice_head(n = 10) |>
  dplyr::mutate(body = stringr::str_replace_all(body, pattern = "\n", " ")) |>
  dplyr::rename(`random message` = body) |>
  knitr::kable(format = "html")
```

### Most Used Words

```{r}
words_data <- rooms$events |>
  dplyr::filter(type == "m.room.message" & !is.na(body)) |>
  tidytext::unnest_tokens(
    output = "word", input = body,
    drop = FALSE
  ) |>
  dplyr::filter(!(word %in% tidytext::stop_words$word))

words_data |>
  dplyr::count(word, sort = T) |>
  dplyr::slice_head(n = 10) |>
  dplyr::mutate(last_used_by = purrr::map_chr(
    word, ~ {
      words_data |>
        dplyr::filter(word == .x) |>
        dplyr::slice_tail(n = 1) |>
        dplyr::pull(sender)
    }
  )) |>
  knitr::kable(format = "html")
```

